---
title: "BIOL390: Assignment 2"
author: "Hailey Buckner"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
something
## Results from an Experiment on Plant Growth

**Description:** Results from an experiment to compare yields (as measured by dried weight of plants) obtained under a control and two different treatment conditions.

**Source:** Dobson, A. J. (1983) _An Introduction to Statistical Modelling_. London: Chapman and Hall.

## Analysis

>>Replace the `XXX` in the code below with the necessary R instructions to give the mean values for each factor level of this dataset in a pretty little table. Hint - the comparison and dataset are the same as in the barplot. You will want to use the function (FUN) of `mean`.

`r knitr::kable(aggregate(mean(c(data, main, las, ylab, xlab, ylim, col))))`

```{r barplot}
boxplot(weight ~ group,                             # compare weight by group
		data = PlantGrowth,                         # built-in data set
		main = "Distribution of Growth Data",       # set title
		las = 1,                                    # rotate y-axis values
        ylab = "Dried weight of plants",            # set y-axis title
		xlab = "Group",                             # set x-axis title
		ylim = c(3,7),                             # set scale of y-axis
		col = c("ivory2","ivory3","ivory4"))        # set bar fill colors
       color = "blue" 
```     

>>Edit the barplot above so that the y-axis range plotted is from 3 to 7 and change the colors of the bars to something that you find fun.

```{r anova, fig.cap="One-way ANOVA of Plant Growth Data"}
knitr::kable(anova(lm(weight ~ group, data = PlantGrowth)),digits = 3)
```

>>The ANOVA analysis is a graph from weight~group information about the specific plant growth.  This also specifies the digit to three. 
